---
title: "R Notebook"
output: html_notebook
---


Libraries
```{r}
library(readr)
library(car)
library(emmeans)
library(tables)
library(tidyverse)
library(RcmdrMisc)
library(dplyr)
```

Read data
```{r}
dd <- read_csv("train.csv")
test <- read_csv("test.csv")

test$epoch <- as.numeric(as.POSIXct(test$epoch))
dd$epoch <- as.numeric(as.POSIXct(dd$epoch))

test$epoch <- test$epoch - min(dd$epoch)
dd$epoch <- dd$epoch - min(dd$epoch)
```


Approximate periods of the sines (each variable with respect to time)
```{r}
TT <- matrix(1:3600, nrow=600)

for (i in 0:599){
   print(i)
   ddi <- filter(dd, sat_id==i)
   testi <- filter(test, sat_id==i)
   tt <- (ddi$epoch[25]-ddi$epoch[1])
  
  
   best_x <- 0
   best_y <- 0
   best_z <- 0
   best_Vx <- 0
   best_Vy <- 0
   best_Vz <- 0
   
   for (k in seq(0.95, 1.05, 0.001)) {
      t <- tt*k
      lmX <- lm(x ~ epoch*sin(2*pi/t*epoch)+epoch*cos(2*pi/t*epoch)+epoch*sin(4*pi/t*epoch)+epoch*cos(4*pi/t*epoch)+epoch*sin(6*pi/t*epoch)+epoch*cos(6*pi/t*epoch)+epoch*sin(8*pi/t*epoch)+epoch*cos(8*pi/t*epoch)+epoch*sin(10*pi/t*epoch)+epoch*cos(10*pi/t*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, ddi)
    
      lmY <- lm(y ~ epoch*sin(2*pi/t*epoch)+epoch*cos(2*pi/t*epoch)+epoch*sin(4*pi/t*epoch)+epoch*cos(4*pi/t*epoch)+epoch*sin(6*pi/t*epoch)+epoch*cos(6*pi/t*epoch)+epoch*sin(8*pi/t*epoch)+epoch*cos(8*pi/t*epoch)+epoch*sin(10*pi/t*epoch)+epoch*cos(10*pi/t*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, ddi)
 
      lmZ <- lm(z ~ epoch*sin(2*pi/t*epoch)+epoch*cos(2*pi/t*epoch)+epoch*sin(4*pi/t*epoch)+epoch*cos(4*pi/t*epoch)+epoch*sin(6*pi/t*epoch)+epoch*cos(6*pi/t*epoch)+epoch*sin(8*pi/t*epoch)+epoch*cos(8*pi/t*epoch)+epoch*sin(10*pi/t*epoch)+epoch*cos(10*pi/t*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, ddi)

      lmVx <- lm(Vx ~ epoch*sin(2*pi/t*epoch)+epoch*cos(2*pi/t*epoch)+epoch*sin(4*pi/t*epoch)+epoch*cos(4*pi/t*epoch)+epoch*sin(6*pi/t*epoch)+epoch*cos(6*pi/t*epoch)+epoch*sin(8*pi/t*epoch)+epoch*cos(8*pi/t*epoch)+epoch*sin(10*pi/t*epoch)+epoch*cos(10*pi/t*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, ddi)
 
      lmVy <- lm(Vy ~ epoch*sin(2*pi/t*epoch)+epoch*cos(2*pi/t*epoch)+epoch*sin(4*pi/t*epoch)+epoch*cos(4*pi/t*epoch)+epoch*sin(6*pi/t*epoch)+epoch*cos(6*pi/t*epoch)+epoch*sin(8*pi/t*epoch)+epoch*cos(8*pi/t*epoch)+epoch*sin(10*pi/t*epoch)+epoch*cos(10*pi/t*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, ddi)
 
      lmVz <- lm(Vz ~ epoch*sin(2*pi/t*epoch)+epoch*cos(2*pi/t*epoch)+epoch*sin(4*pi/t*epoch)+epoch*cos(4*pi/t*epoch)+epoch*sin(6*pi/t*epoch)+epoch*cos(6*pi/t*epoch)+epoch*sin(8*pi/t*epoch)+epoch*cos(8*pi/t*epoch)+epoch*sin(10*pi/t*epoch)+epoch*cos(10*pi/t*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, ddi)
     
      if (summary(lmX)$adj.r.squared > best_x) {
        best_x <- summary(lmX)$adj.r.squared
        TT[i+1, 1] <- t
      }
   
      if (summary(lmY)$adj.r.squared > best_y) {
        best_y <- summary(lmY)$adj.r.squared
        TT[i+1, 2] <- t
      }
   
      if (summary(lmZ)$adj.r.squared > best_z) {
        best_z <- summary(lmZ)$adj.r.squared
        TT[i+1, 3] <- t
      }
   
      if (summary(lmVx)$adj.r.squared > best_Vx) {
        best_Vx <- summary(lmVx)$adj.r.squared
        TT[i+1, 4] <- t
      }
   
      if (summary(lmVy)$adj.r.squared > best_Vy) {
        best_Vy <- summary(lmVy)$adj.r.squared
        TT[i+1, 5] <- t
      }
   
      if (summary(lmVz)$adj.r.squared > best_Vz) {
        best_Vz <- summary(lmVz)$adj.r.squared
        TT[i+1, 6] <- t
      }
  }
}

write.csv(TT, "periods3.csv", quote = F, row.names = F)
```


Make better approximations for the periods
```{r}
TT <- read.csv("periods3.csv")

for (i in 0:599){
   print(i)
   ddi <- filter(dd, sat_id==i)
   testi <- filter(test, sat_id==i)
   
   tt1 <- unlist(TT[i+1,1])
   tt2 <- unlist(TT[i+1,2])
   tt3 <- unlist(TT[i+1,3])
   tt4 <- unlist(TT[i+1,4])
   tt5 <- unlist(TT[i+1,5])
   tt6 <- unlist(TT[i+1,6])
  
  
   best_x <- 0
   best_y <- 0
   best_z <- 0
   best_Vx <- 0
   best_Vy <- 0
   best_Vz <- 0
   
   for (k in seq(0.995, 1.005, 0.0001)) {
      t1 <- tt1*k
      t2 <- tt2*k
      t3 <- tt3*k
      t4 <- tt4*k
      t5 <- tt5*k
      t6 <- tt6*k
      
      lmX <- lm(x ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, ddi)
    
      lmY <- lm(y ~ epoch*sin(2*pi/t2*epoch)+epoch*cos(2*pi/t2*epoch)+epoch*sin(4*pi/t2*epoch)+epoch*cos(4*pi/t2*epoch)+epoch*sin(6*pi/t2*epoch)+epoch*cos(6*pi/t2*epoch)+epoch*sin(8*pi/t2*epoch)+epoch*cos(8*pi/t2*epoch)+epoch*sin(10*pi/t2*epoch)+epoch*cos(10*pi/t2*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, ddi)
 
      lmZ <- lm(z ~ epoch*sin(2*pi/t3*epoch)+epoch*cos(2*pi/t3*epoch)+epoch*sin(4*pi/t3*epoch)+epoch*cos(4*pi/t3*epoch)+epoch*sin(6*pi/t3*epoch)+epoch*cos(6*pi/t3*epoch)+epoch*sin(8*pi/t3*epoch)+epoch*cos(8*pi/t3*epoch)+epoch*sin(10*pi/t3*epoch)+epoch*cos(10*pi/t3*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, ddi)

      lmVx <- lm(Vx ~ epoch*sin(2*pi/t4*epoch)+epoch*cos(2*pi/t4*epoch)+epoch*sin(4*pi/t4*epoch)+epoch*cos(4*pi/t4*epoch)+epoch*sin(6*pi/t4*epoch)+epoch*cos(6*pi/t4*epoch)+epoch*sin(8*pi/t4*epoch)+epoch*cos(8*pi/t4*epoch)+epoch*sin(10*pi/t4*epoch)+epoch*cos(10*pi/t4*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, ddi)
 
      lmVy <- lm(Vy ~ epoch*sin(2*pi/t5*epoch)+epoch*cos(2*pi/t5*epoch)+epoch*sin(4*pi/t5*epoch)+epoch*cos(4*pi/t5*epoch)+epoch*sin(6*pi/t5*epoch)+epoch*cos(6*pi/t5*epoch)+epoch*sin(8*pi/t5*epoch)+epoch*cos(8*pi/t5*epoch)+epoch*sin(10*pi/t5*epoch)+epoch*cos(10*pi/t5*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, ddi)
 
      lmVz <- lm(Vz ~ epoch*sin(2*pi/t6*epoch)+epoch*cos(2*pi/t6*epoch)+epoch*sin(4*pi/t6*epoch)+epoch*cos(4*pi/t6*epoch)+epoch*sin(6*pi/t6*epoch)+epoch*cos(6*pi/t6*epoch)+epoch*sin(8*pi/t6*epoch)+epoch*cos(8*pi/t6*epoch)+epoch*sin(10*pi/t6*epoch)+epoch*cos(10*pi/t6*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, ddi)
     
      if (summary(lmX)$adj.r.squared > best_x) {
        best_x <- summary(lmX)$adj.r.squared
        TT[i+1, 1] <- t1
      }
   
      if (summary(lmY)$adj.r.squared > best_y) {
        best_y <- summary(lmY)$adj.r.squared
        TT[i+1, 2] <- t2
      }
   
      if (summary(lmZ)$adj.r.squared > best_z) {
        best_z <- summary(lmZ)$adj.r.squared
        TT[i+1, 3] <- t3
      }
   
      if (summary(lmVx)$adj.r.squared > best_Vx) {
        best_Vx <- summary(lmVx)$adj.r.squared
        TT[i+1, 4] <- t4
      }
   
      if (summary(lmVy)$adj.r.squared > best_Vy) {
        best_Vy <- summary(lmVy)$adj.r.squared
        TT[i+1, 5] <- t5
      }
   
      if (summary(lmVz)$adj.r.squared > best_Vz) {
        best_Vz <- summary(lmVz)$adj.r.squared
        TT[i+1, 6] <- t6
      }
  }
}

write.csv(TT, "periods2.csv", quote = F, row.names = F)
```




Make even better approximations for the periods
```{r}
TT <- read.csv("periods2.csv")

for (i in 0:599){
   print(i)
   ddi <- filter(dd, sat_id==i)
   testi <- filter(test, sat_id==i)
   
   tt1 <- unlist(TT[i+1,1])
   tt2 <- unlist(TT[i+1,2])
   tt3 <- unlist(TT[i+1,3])
   tt4 <- unlist(TT[i+1,4])
   tt5 <- unlist(TT[i+1,5])
   tt6 <- unlist(TT[i+1,6])
  
  
   best_x <- 0
   best_y <- 0
   best_z <- 0
   best_Vx <- 0
   best_Vy <- 0
   best_Vz <- 0
   
   for (k in seq(0.9995, 1.0005, 0.00001)) {
      t1 <- tt1*k
      t2 <- tt2*k
      t3 <- tt3*k
      t4 <- tt4*k
      t5 <- tt5*k
      t6 <- tt6*k
      
      lmX <- lm(x ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, ddi)
    
      lmY <- lm(y ~ epoch*sin(2*pi/t2*epoch)+epoch*cos(2*pi/t2*epoch)+epoch*sin(4*pi/t2*epoch)+epoch*cos(4*pi/t2*epoch)+epoch*sin(6*pi/t2*epoch)+epoch*cos(6*pi/t2*epoch)+epoch*sin(8*pi/t2*epoch)+epoch*cos(8*pi/t2*epoch)+epoch*sin(10*pi/t2*epoch)+epoch*cos(10*pi/t2*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, ddi)
 
      lmZ <- lm(z ~ epoch*sin(2*pi/t3*epoch)+epoch*cos(2*pi/t3*epoch)+epoch*sin(4*pi/t3*epoch)+epoch*cos(4*pi/t3*epoch)+epoch*sin(6*pi/t3*epoch)+epoch*cos(6*pi/t3*epoch)+epoch*sin(8*pi/t3*epoch)+epoch*cos(8*pi/t3*epoch)+epoch*sin(10*pi/t3*epoch)+epoch*cos(10*pi/t3*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, ddi)

      lmVx <- lm(Vx ~ epoch*sin(2*pi/t4*epoch)+epoch*cos(2*pi/t4*epoch)+epoch*sin(4*pi/t4*epoch)+epoch*cos(4*pi/t4*epoch)+epoch*sin(6*pi/t4*epoch)+epoch*cos(6*pi/t4*epoch)+epoch*sin(8*pi/t4*epoch)+epoch*cos(8*pi/t4*epoch)+epoch*sin(10*pi/t4*epoch)+epoch*cos(10*pi/t4*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, ddi)
 
      lmVy <- lm(Vy ~ epoch*sin(2*pi/t5*epoch)+epoch*cos(2*pi/t5*epoch)+epoch*sin(4*pi/t5*epoch)+epoch*cos(4*pi/t5*epoch)+epoch*sin(6*pi/t5*epoch)+epoch*cos(6*pi/t5*epoch)+epoch*sin(8*pi/t5*epoch)+epoch*cos(8*pi/t5*epoch)+epoch*sin(10*pi/t5*epoch)+epoch*cos(10*pi/t5*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, ddi)
 
      lmVz <- lm(Vz ~ epoch*sin(2*pi/t6*epoch)+epoch*cos(2*pi/t6*epoch)+epoch*sin(4*pi/t6*epoch)+epoch*cos(4*pi/t6*epoch)+epoch*sin(6*pi/t6*epoch)+epoch*cos(6*pi/t6*epoch)+epoch*sin(8*pi/t6*epoch)+epoch*cos(8*pi/t6*epoch)+epoch*sin(10*pi/t6*epoch)+epoch*cos(10*pi/t6*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, ddi)
     
      if (summary(lmX)$adj.r.squared > best_x) {
        best_x <- summary(lmX)$adj.r.squared
        TT[i+1, 1] <- t1
      }
   
      if (summary(lmY)$adj.r.squared > best_y) {
        best_y <- summary(lmY)$adj.r.squared
        TT[i+1, 2] <- t2
      }
   
      if (summary(lmZ)$adj.r.squared > best_z) {
        best_z <- summary(lmZ)$adj.r.squared
        TT[i+1, 3] <- t3
      }
   
      if (summary(lmVx)$adj.r.squared > best_Vx) {
        best_Vx <- summary(lmVx)$adj.r.squared
        TT[i+1, 4] <- t4
      }
   
      if (summary(lmVy)$adj.r.squared > best_Vy) {
        best_Vy <- summary(lmVy)$adj.r.squared
        TT[i+1, 5] <- t5
      }
   
      if (summary(lmVz)$adj.r.squared > best_Vz) {
        best_Vz <- summary(lmVz)$adj.r.squared
        TT[i+1, 6] <- t6
      }
  }
}

write.csv(TT, "periods.csv", quote = F, row.names = F)
```


Get last periods
```{r}
TT <- read_csv("periods.csv")
```


Score function for crossvalidation
```{r}
score <- function(val_pred, val_real) {
  smape <- mean(abs(val_pred - val_real) / (abs(val_pred)+abs(val_real)))
  100 * (1 - smape)
}
```



Function if pred is false, returns the crossvalidation for the model, if pred is true returns the prediction using that model
```{r}
model <- function(sat, coord, num_model, pred=F) {
  t1 <- unlist(TT[sat+1,coord])
  if (!pred) {
    tr <- dd %>% filter(sat_id == sat)
  
    total <- length(tr$epoch)
    limit <- as.integer(0.8 * total)
    
    val <- tr[limit:total,]
    tr <- tr[1:(limit-1),]
    tr2 <- tr[as.integer(length(tr$id)*0.1):length(tr$id),]
    tr3 <- tr[as.integer(length(tr$id)*0.25):length(tr$id),]
    tr4 <- tr[as.integer(length(tr$id)*0.5):length(tr$id),]
    
    tr$aux <- unlist(tr[,coord+3])
    tr2$aux <- unlist(tr2[,coord+3])
    tr3$aux <- unlist(tr3[,coord+3])
    tr4$aux <- unlist(tr4[,coord+3])
    val$aux <- unlist(val[,coord+3])
  } else {
    tr <- dd %>% filter(sat_id == sat)
    tst <- test %>% filter(sat_id == sat)
    tr2 <- tr[as.integer(length(tr$id)*0.1):length(tr$id),]
    tr3 <- tr[as.integer(length(tr$id)*0.25):length(tr$id),]
    tr4 <- tr[as.integer(length(tr$id)*0.5):length(tr$id),]
    
    tr$aux <- unlist(tr[,coord+3])
    tst$aux <- unlist(tst[,coord+3])
    tr2$aux <- unlist(tr2[,coord+3])
    tr3$aux <- unlist(tr3[,coord+3])
    tr4$aux <- unlist(tr4[,coord+3])    
    
  }
  
  #modelos iniciales
          if (num_model == 1) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr)
    } else if (num_model == 2) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch), tr)
    } else if (num_model == 3) {
        lmX <- lm(aux ~ epoch+epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+epoch*x_sim+epoch*y_sim+epoch*z_sim+epoch*Vx_sim+epoch*Vy_sim+epoch*Vz_sim, tr)
    } else if (num_model == 4) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr)
    } else if (num_model == 5) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch), tr)
    } 
  
  
  #con tr2
  #modelo lineal
  else if (num_model == 6) {
        lmX <- lm(aux ~ x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr2)
  }
  
  #3 armónicos
      else if (num_model == 7) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr2)
    } else if (num_model == 8) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch), tr2)
    } else if (num_model == 9) {
        lmX <- lm(aux ~ epoch+epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+epoch*x_sim+epoch*y_sim+epoch*z_sim+epoch*Vx_sim+epoch*Vy_sim+epoch*Vz_sim, tr2)
    } else if (num_model == 10) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr2)
    } else if (num_model == 11) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch), tr2)
    }
  
  #4 armónicos
      else if (num_model == 12) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr2)
    } else if (num_model == 13) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch), tr2)
    } else if (num_model == 14) {
        lmX <- lm(aux ~ epoch+epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+epoch*x_sim+epoch*y_sim+epoch*z_sim+epoch*Vx_sim+epoch*Vy_sim+epoch*Vz_sim, tr2)
    } else if (num_model == 15) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr2)
    } else if (num_model == 16) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch), tr2)
    }
    
  #5 armónicos
      else if (num_model == 17) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr2)
    } else if (num_model == 18) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch), tr2)
    } else if (num_model == 19) {
        lmX <- lm(aux ~ epoch+epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+epoch*x_sim+epoch*y_sim+epoch*z_sim+epoch*Vx_sim+epoch*Vy_sim+epoch*Vz_sim, tr2)
    } else if (num_model == 20) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr2)
    } else if (num_model == 21) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch), tr2)
    }
  
  #6 armónicos
      else if (num_model == 22) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr2)
    } else if (num_model == 23) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch), tr2)
    } else if (num_model == 24) {
        lmX <- lm(aux ~ epoch+epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*x_sim+epoch*y_sim+epoch*z_sim+epoch*Vx_sim+epoch*Vy_sim+epoch*Vz_sim, tr2)
    } else if (num_model == 25) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+sin(12*pi/t1*epoch)+cos(12*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr2)
    } else if (num_model == 26) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+sin(12*pi/t1*epoch)+cos(12*pi/t1*epoch), tr2)
    }
  
  #7 armónicos
      else if (num_model == 27) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr2)
    } else if (num_model == 28) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch), tr2)
    } else if (num_model == 29) {
        lmX <- lm(aux ~ epoch+epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+epoch*x_sim+epoch*y_sim+epoch*z_sim+epoch*Vx_sim+epoch*Vy_sim+epoch*Vz_sim, tr2)
    } else if (num_model == 30) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+sin(12*pi/t1*epoch)+cos(12*pi/t1*epoch)+sin(14*pi/t1*epoch)+cos(14*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr2)
    } else if (num_model == 31) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+sin(12*pi/t1*epoch)+cos(12*pi/t1*epoch)+sin(14*pi/t1*epoch)+cos(14*pi/t1*epoch), tr2)
    }
  
  #8 armónicos
      else if (num_model == 32) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+epoch*sin(16*pi/t1*epoch)+epoch*cos(16*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr2)
    } else if (num_model == 33) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+epoch*sin(16*pi/t1*epoch)+epoch*cos(16*pi/t1*epoch), tr2)
    } else if (num_model == 34) {
        lmX <- lm(aux ~ epoch+epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+epoch*sin(16*pi/t1*epoch)+epoch*cos(16*pi/t1*epoch)+epoch*x_sim+epoch*y_sim+epoch*z_sim+epoch*Vx_sim+epoch*Vy_sim+epoch*Vz_sim, tr2)
    } else if (num_model == 35) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+sin(12*pi/t1*epoch)+cos(12*pi/t1*epoch)+sin(14*pi/t1*epoch)+cos(14*pi/t1*epoch)+sin(16*pi/t1*epoch)+cos(16*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr2)
    } else if (num_model == 36) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+sin(12*pi/t1*epoch)+cos(12*pi/t1*epoch)+sin(14*pi/t1*epoch)+cos(14*pi/t1*epoch)+sin(16*pi/t1*epoch)+cos(16*pi/t1*epoch), tr2)
    }
  
  #9 armónios
      else if (num_model == 37) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+epoch*sin(16*pi/t1*epoch)+epoch*cos(16*pi/t1*epoch)+epoch*sin(18*pi/t1*epoch)+epoch*cos(18*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr2)
    } else if (num_model == 38) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+epoch*sin(16*pi/t1*epoch)+epoch*cos(16*pi/t1*epoch)+epoch*sin(18*pi/t1*epoch)+epoch*cos(18*pi/t1*epoch), tr2)
    } else if (num_model == 39) {
        lmX <- lm(aux ~ epoch+epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+epoch*sin(16*pi/t1*epoch)+epoch*cos(16*pi/t1*epoch)+epoch*sin(18*pi/t1*epoch)+epoch*cos(18*pi/t1*epoch)+epoch*x_sim+epoch*y_sim+epoch*z_sim+epoch*Vx_sim+epoch*Vy_sim+epoch*Vz_sim, tr2)
    } else if (num_model == 40) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+sin(12*pi/t1*epoch)+cos(12*pi/t1*epoch)+sin(14*pi/t1*epoch)+cos(14*pi/t1*epoch)+sin(16*pi/t1*epoch)+cos(16*pi/t1*epoch)+sin(18*pi/t1*epoch)+cos(18*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr2)
    } else if (num_model == 41) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+sin(12*pi/t1*epoch)+cos(12*pi/t1*epoch)+sin(14*pi/t1*epoch)+cos(14*pi/t1*epoch)+sin(16*pi/t1*epoch)+cos(16*pi/t1*epoch)+sin(18*pi/t1*epoch)+cos(18*pi/t1*epoch), tr2)
    }
  
  #10 armónicos
      else if (num_model == 42) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+epoch*sin(16*pi/t1*epoch)+epoch*cos(16*pi/t1*epoch)+epoch*sin(18*pi/t1*epoch)+epoch*cos(18*pi/t1*epoch)+epoch*sin(20*pi/t1*epoch)+epoch*cos(20*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr2)
    } else if (num_model == 43) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+epoch*sin(16*pi/t1*epoch)+epoch*cos(16*pi/t1*epoch)+epoch*sin(18*pi/t1*epoch)+epoch*cos(18*pi/t1*epoch)+epoch*sin(20*pi/t1*epoch)+epoch*cos(20*pi/t1*epoch), tr2)
    } else if (num_model == 44) {
        lmX <- lm(aux ~ epoch+epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+epoch*sin(16*pi/t1*epoch)+epoch*cos(16*pi/t1*epoch)+epoch*sin(18*pi/t1*epoch)+epoch*cos(18*pi/t1*epoch)+epoch*sin(20*pi/t1*epoch)+epoch*cos(20*pi/t1*epoch)+epoch*x_sim+epoch*y_sim+epoch*z_sim+epoch*Vx_sim+epoch*Vy_sim+epoch*Vz_sim, tr2)
    } else if (num_model == 45) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+sin(12*pi/t1*epoch)+cos(12*pi/t1*epoch)+sin(14*pi/t1*epoch)+cos(14*pi/t1*epoch)+sin(16*pi/t1*epoch)+cos(16*pi/t1*epoch)+sin(18*pi/t1*epoch)+cos(18*pi/t1*epoch)+sin(20*pi/t1*epoch)+cos(20*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr2)
    } else if (num_model == 46) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+sin(12*pi/t1*epoch)+cos(12*pi/t1*epoch)+sin(14*pi/t1*epoch)+cos(14*pi/t1*epoch)+sin(16*pi/t1*epoch)+cos(16*pi/t1*epoch)+sin(18*pi/t1*epoch)+cos(18*pi/t1*epoch)+sin(20*pi/t1*epoch)+cos(20*pi/t1*epoch), tr2)
    }#con tr2
  #modelo lineal
  else if (num_model == 47) {
        lmX <- lm(aux ~ x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr2)
  }
  
  #3 armónicos
      else if (num_model == 48) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr)
    } else if (num_model == 49) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch), tr)
    } else if (num_model == 50) {
        lmX <- lm(aux ~ epoch+epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+epoch*x_sim+epoch*y_sim+epoch*z_sim+epoch*Vx_sim+epoch*Vy_sim+epoch*Vz_sim, tr)
    } else if (num_model == 51) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr)
    } else if (num_model == 52) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch), tr)
    }
  
  #4 armónicos
      else if (num_model == 53) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr)
    } else if (num_model == 54) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch), tr)
    } else if (num_model == 55) {
        lmX <- lm(aux ~ epoch+epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+epoch*x_sim+epoch*y_sim+epoch*z_sim+epoch*Vx_sim+epoch*Vy_sim+epoch*Vz_sim, tr)
    } else if (num_model == 56) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr)
    } else if (num_model == 57) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch), tr)
    }
    
  #5 armónicos
      else if (num_model == 58) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr)
    } else if (num_model == 59) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch), tr)
    } else if (num_model == 60) {
        lmX <- lm(aux ~ epoch+epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+epoch*x_sim+epoch*y_sim+epoch*z_sim+epoch*Vx_sim+epoch*Vy_sim+epoch*Vz_sim, tr)
    } else if (num_model == 61) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr)
    } else if (num_model == 62) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch), tr)
    }
  
  #6 armónicos
      else if (num_model == 63) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr)
    } else if (num_model == 64) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch), tr)
    } else if (num_model == 65) {
        lmX <- lm(aux ~ epoch+epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*x_sim+epoch*y_sim+epoch*z_sim+epoch*Vx_sim+epoch*Vy_sim+epoch*Vz_sim, tr)
    } else if (num_model == 66) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+sin(12*pi/t1*epoch)+cos(12*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr)
    } else if (num_model == 67) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+sin(12*pi/t1*epoch)+cos(12*pi/t1*epoch), tr)
    }
  
  #7 armónicos
      else if (num_model == 68) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr)
    } else if (num_model == 69) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch), tr)
    } else if (num_model == 70) {
        lmX <- lm(aux ~ epoch+epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+epoch*x_sim+epoch*y_sim+epoch*z_sim+epoch*Vx_sim+epoch*Vy_sim+epoch*Vz_sim, tr)
    } else if (num_model == 71) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+sin(12*pi/t1*epoch)+cos(12*pi/t1*epoch)+sin(14*pi/t1*epoch)+cos(14*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr)
    } else if (num_model == 72) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+sin(12*pi/t1*epoch)+cos(12*pi/t1*epoch)+sin(14*pi/t1*epoch)+cos(14*pi/t1*epoch), tr)
    }
  
  #8 armónicos
      else if (num_model == 73) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+epoch*sin(16*pi/t1*epoch)+epoch*cos(16*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr)
    } else if (num_model == 74) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+epoch*sin(16*pi/t1*epoch)+epoch*cos(16*pi/t1*epoch), tr)
    } else if (num_model == 75) {
        lmX <- lm(aux ~ epoch+epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+epoch*sin(16*pi/t1*epoch)+epoch*cos(16*pi/t1*epoch)+epoch*x_sim+epoch*y_sim+epoch*z_sim+epoch*Vx_sim+epoch*Vy_sim+epoch*Vz_sim, tr)
    } else if (num_model == 76) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+sin(12*pi/t1*epoch)+cos(12*pi/t1*epoch)+sin(14*pi/t1*epoch)+cos(14*pi/t1*epoch)+sin(16*pi/t1*epoch)+cos(16*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr)
    } else if (num_model == 77) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+sin(12*pi/t1*epoch)+cos(12*pi/t1*epoch)+sin(14*pi/t1*epoch)+cos(14*pi/t1*epoch)+sin(16*pi/t1*epoch)+cos(16*pi/t1*epoch), tr)
    }
  
  #9 armónios
      else if (num_model == 78) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+epoch*sin(16*pi/t1*epoch)+epoch*cos(16*pi/t1*epoch)+epoch*sin(18*pi/t1*epoch)+epoch*cos(18*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr)
    } else if (num_model == 79) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+epoch*sin(16*pi/t1*epoch)+epoch*cos(16*pi/t1*epoch)+epoch*sin(18*pi/t1*epoch)+epoch*cos(18*pi/t1*epoch), tr)
    } else if (num_model == 80) {
        lmX <- lm(aux ~ epoch+epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+epoch*sin(16*pi/t1*epoch)+epoch*cos(16*pi/t1*epoch)+epoch*sin(18*pi/t1*epoch)+epoch*cos(18*pi/t1*epoch)+epoch*x_sim+epoch*y_sim+epoch*z_sim+epoch*Vx_sim+epoch*Vy_sim+epoch*Vz_sim, tr)
    } else if (num_model == 81) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+sin(12*pi/t1*epoch)+cos(12*pi/t1*epoch)+sin(14*pi/t1*epoch)+cos(14*pi/t1*epoch)+sin(16*pi/t1*epoch)+cos(16*pi/t1*epoch)+sin(18*pi/t1*epoch)+cos(18*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr)
    } else if (num_model == 82) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+sin(12*pi/t1*epoch)+cos(12*pi/t1*epoch)+sin(14*pi/t1*epoch)+cos(14*pi/t1*epoch)+sin(16*pi/t1*epoch)+cos(16*pi/t1*epoch)+sin(18*pi/t1*epoch)+cos(18*pi/t1*epoch), tr)
    }
  
  #10 armónicos
      else if (num_model == 83) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+epoch*sin(16*pi/t1*epoch)+epoch*cos(16*pi/t1*epoch)+epoch*sin(18*pi/t1*epoch)+epoch*cos(18*pi/t1*epoch)+epoch*sin(20*pi/t1*epoch)+epoch*cos(20*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr)
    } else if (num_model == 84) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+epoch*sin(16*pi/t1*epoch)+epoch*cos(16*pi/t1*epoch)+epoch*sin(18*pi/t1*epoch)+epoch*cos(18*pi/t1*epoch)+epoch*sin(20*pi/t1*epoch)+epoch*cos(20*pi/t1*epoch), tr)
    } else if (num_model == 85) {
        lmX <- lm(aux ~ epoch+epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+epoch*sin(16*pi/t1*epoch)+epoch*cos(16*pi/t1*epoch)+epoch*sin(18*pi/t1*epoch)+epoch*cos(18*pi/t1*epoch)+epoch*sin(20*pi/t1*epoch)+epoch*cos(20*pi/t1*epoch)+epoch*x_sim+epoch*y_sim+epoch*z_sim+epoch*Vx_sim+epoch*Vy_sim+epoch*Vz_sim, tr)
    } else if (num_model == 86) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+sin(12*pi/t1*epoch)+cos(12*pi/t1*epoch)+sin(14*pi/t1*epoch)+cos(14*pi/t1*epoch)+sin(16*pi/t1*epoch)+cos(16*pi/t1*epoch)+sin(18*pi/t1*epoch)+cos(18*pi/t1*epoch)+sin(20*pi/t1*epoch)+cos(20*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr)
    } else if (num_model == 87) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+sin(12*pi/t1*epoch)+cos(12*pi/t1*epoch)+sin(14*pi/t1*epoch)+cos(14*pi/t1*epoch)+sin(16*pi/t1*epoch)+cos(16*pi/t1*epoch)+sin(18*pi/t1*epoch)+cos(18*pi/t1*epoch)+sin(20*pi/t1*epoch)+cos(20*pi/t1*epoch), tr)
    }
    
  else if (num_model == 88) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr3)
    } else if (num_model == 89) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch), tr3)
    } else if (num_model == 90) {
        lmX <- lm(aux ~ epoch+epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+epoch*x_sim+epoch*y_sim+epoch*z_sim+epoch*Vx_sim+epoch*Vy_sim+epoch*Vz_sim, tr3)
    } else if (num_model == 91) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr3)
    } else if (num_model == 92) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch), tr3)
    }
  
  #4 armónicos
      else if (num_model == 93) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr3)
    } else if (num_model == 94) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch), tr3)
    } else if (num_model == 95) {
        lmX <- lm(aux ~ epoch+epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+epoch*x_sim+epoch*y_sim+epoch*z_sim+epoch*Vx_sim+epoch*Vy_sim+epoch*Vz_sim, tr3)
    } else if (num_model == 96) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr3)
    } else if (num_model == 97) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch), tr3)
    }
    
  #5 armónicos
      else if (num_model == 98) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr3)
    } else if (num_model == 99) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch), tr3)
    } else if (num_model == 100) {
        lmX <- lm(aux ~ epoch+epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+epoch*x_sim+epoch*y_sim+epoch*z_sim+epoch*Vx_sim+epoch*Vy_sim+epoch*Vz_sim, tr3)
    } else if (num_model == 101) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr3)
    } else if (num_model == 102) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch), tr3)
    }
  
  #6 armónicos
      else if (num_model == 103) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr3)
    } else if (num_model == 104) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch), tr3)
    } else if (num_model == 105) {
        lmX <- lm(aux ~ epoch+epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*x_sim+epoch*y_sim+epoch*z_sim+epoch*Vx_sim+epoch*Vy_sim+epoch*Vz_sim, tr3)
    } else if (num_model == 106) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+sin(12*pi/t1*epoch)+cos(12*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr3)
    } else if (num_model == 107) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+sin(12*pi/t1*epoch)+cos(12*pi/t1*epoch), tr3)
    }
  
  #7 armónicos
      else if (num_model == 108) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr3)
    } else if (num_model == 109) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch), tr3)
    } else if (num_model == 110) {
        lmX <- lm(aux ~ epoch+epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+epoch*x_sim+epoch*y_sim+epoch*z_sim+epoch*Vx_sim+epoch*Vy_sim+epoch*Vz_sim, tr3)
    } else if (num_model == 111) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+sin(12*pi/t1*epoch)+cos(12*pi/t1*epoch)+sin(14*pi/t1*epoch)+cos(14*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr3)
    } else if (num_model == 112) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+sin(12*pi/t1*epoch)+cos(12*pi/t1*epoch)+sin(14*pi/t1*epoch)+cos(14*pi/t1*epoch), tr3)
    }
  
  #8 armónicos
      else if (num_model == 113) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+epoch*sin(16*pi/t1*epoch)+epoch*cos(16*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr3)
    } else if (num_model == 114) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+epoch*sin(16*pi/t1*epoch)+epoch*cos(16*pi/t1*epoch), tr3)
    } else if (num_model == 115) {
        lmX <- lm(aux ~ epoch+epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+epoch*sin(16*pi/t1*epoch)+epoch*cos(16*pi/t1*epoch)+epoch*x_sim+epoch*y_sim+epoch*z_sim+epoch*Vx_sim+epoch*Vy_sim+epoch*Vz_sim, tr3)
    } else if (num_model == 116) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+sin(12*pi/t1*epoch)+cos(12*pi/t1*epoch)+sin(14*pi/t1*epoch)+cos(14*pi/t1*epoch)+sin(16*pi/t1*epoch)+cos(16*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr3)
    } else if (num_model == 117) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+sin(12*pi/t1*epoch)+cos(12*pi/t1*epoch)+sin(14*pi/t1*epoch)+cos(14*pi/t1*epoch)+sin(16*pi/t1*epoch)+cos(16*pi/t1*epoch), tr3)
    }
  
  #9 armónios
      else if (num_model == 118) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+epoch*sin(16*pi/t1*epoch)+epoch*cos(16*pi/t1*epoch)+epoch*sin(18*pi/t1*epoch)+epoch*cos(18*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr3)
    } else if (num_model == 119) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+epoch*sin(16*pi/t1*epoch)+epoch*cos(16*pi/t1*epoch)+epoch*sin(18*pi/t1*epoch)+epoch*cos(18*pi/t1*epoch), tr3)
    } else if (num_model == 120) {
        lmX <- lm(aux ~ epoch+epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+epoch*sin(16*pi/t1*epoch)+epoch*cos(16*pi/t1*epoch)+epoch*sin(18*pi/t1*epoch)+epoch*cos(18*pi/t1*epoch)+epoch*x_sim+epoch*y_sim+epoch*z_sim+epoch*Vx_sim+epoch*Vy_sim+epoch*Vz_sim, tr3)
    } else if (num_model == 121) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+sin(12*pi/t1*epoch)+cos(12*pi/t1*epoch)+sin(14*pi/t1*epoch)+cos(14*pi/t1*epoch)+sin(16*pi/t1*epoch)+cos(16*pi/t1*epoch)+sin(18*pi/t1*epoch)+cos(18*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr3)
    } else if (num_model == 122) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+sin(12*pi/t1*epoch)+cos(12*pi/t1*epoch)+sin(14*pi/t1*epoch)+cos(14*pi/t1*epoch)+sin(16*pi/t1*epoch)+cos(16*pi/t1*epoch)+sin(18*pi/t1*epoch)+cos(18*pi/t1*epoch), tr3)
    }
  
  #10 armónicos
      else if (num_model == 123) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+epoch*sin(16*pi/t1*epoch)+epoch*cos(16*pi/t1*epoch)+epoch*sin(18*pi/t1*epoch)+epoch*cos(18*pi/t1*epoch)+epoch*sin(20*pi/t1*epoch)+epoch*cos(20*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr3)
    } else if (num_model == 124) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+epoch*sin(16*pi/t1*epoch)+epoch*cos(16*pi/t1*epoch)+epoch*sin(18*pi/t1*epoch)+epoch*cos(18*pi/t1*epoch)+epoch*sin(20*pi/t1*epoch)+epoch*cos(20*pi/t1*epoch), tr3)
    } else if (num_model == 125) {
        lmX <- lm(aux ~ epoch+epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+epoch*sin(16*pi/t1*epoch)+epoch*cos(16*pi/t1*epoch)+epoch*sin(18*pi/t1*epoch)+epoch*cos(18*pi/t1*epoch)+epoch*sin(20*pi/t1*epoch)+epoch*cos(20*pi/t1*epoch)+epoch*x_sim+epoch*y_sim+epoch*z_sim+epoch*Vx_sim+epoch*Vy_sim+epoch*Vz_sim, tr3)
    } else if (num_model == 126) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+sin(12*pi/t1*epoch)+cos(12*pi/t1*epoch)+sin(14*pi/t1*epoch)+cos(14*pi/t1*epoch)+sin(16*pi/t1*epoch)+cos(16*pi/t1*epoch)+sin(18*pi/t1*epoch)+cos(18*pi/t1*epoch)+sin(20*pi/t1*epoch)+cos(20*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr3)
    } else if (num_model == 127) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+sin(12*pi/t1*epoch)+cos(12*pi/t1*epoch)+sin(14*pi/t1*epoch)+cos(14*pi/t1*epoch)+sin(16*pi/t1*epoch)+cos(16*pi/t1*epoch)+sin(18*pi/t1*epoch)+cos(18*pi/t1*epoch)+sin(20*pi/t1*epoch)+cos(20*pi/t1*epoch), tr3)
    }
  
  else if (num_model == 128) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr4)
    } else if (num_model == 129) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch), tr4)
    } else if (num_model == 130) {
        lmX <- lm(aux ~ epoch+epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+epoch*x_sim+epoch*y_sim+epoch*z_sim+epoch*Vx_sim+epoch*Vy_sim+epoch*Vz_sim, tr4)
    } else if (num_model == 131) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr4)
    } else if (num_model == 132) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch), tr4)
    }
  
  #4 armónicos
      else if (num_model == 133) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr4)
    } else if (num_model == 134) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch), tr4)
    } else if (num_model == 135) {
        lmX <- lm(aux ~ epoch+epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+epoch*x_sim+epoch*y_sim+epoch*z_sim+epoch*Vx_sim+epoch*Vy_sim+epoch*Vz_sim, tr4)
    } else if (num_model == 136) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr4)
    } else if (num_model == 137) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch), tr4)
    }
    
  #5 armónicos
      else if (num_model == 138) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr4)
    } else if (num_model == 139) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch), tr4)
    } else if (num_model == 140) {
        lmX <- lm(aux ~ epoch+epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+epoch*x_sim+epoch*y_sim+epoch*z_sim+epoch*Vx_sim+epoch*Vy_sim+epoch*Vz_sim, tr4)
    } else if (num_model == 141) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr4)
    } else if (num_model == 142) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch), tr4)
    }
  
  #6 armónicos
      else if (num_model == 143) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr4)
    } else if (num_model == 144) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch), tr4)
    } else if (num_model == 145) {
        lmX <- lm(aux ~ epoch+epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*x_sim+epoch*y_sim+epoch*z_sim+epoch*Vx_sim+epoch*Vy_sim+epoch*Vz_sim, tr4)
    } else if (num_model == 146) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+sin(12*pi/t1*epoch)+cos(12*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr4)
    } else if (num_model == 147) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+sin(12*pi/t1*epoch)+cos(12*pi/t1*epoch), tr4)
    }
  
  #7 armónicos
      else if (num_model == 148) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr4)
    } else if (num_model == 149) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch), tr4)
    } else if (num_model == 150) {
        lmX <- lm(aux ~ epoch+epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+epoch*x_sim+epoch*y_sim+epoch*z_sim+epoch*Vx_sim+epoch*Vy_sim+epoch*Vz_sim, tr4)
    } else if (num_model == 151) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+sin(12*pi/t1*epoch)+cos(12*pi/t1*epoch)+sin(14*pi/t1*epoch)+cos(14*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr4)
    } else if (num_model == 152) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+sin(12*pi/t1*epoch)+cos(12*pi/t1*epoch)+sin(14*pi/t1*epoch)+cos(14*pi/t1*epoch), tr4)
    }
  
  #8 armónicos
      else if (num_model == 153) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+epoch*sin(16*pi/t1*epoch)+epoch*cos(16*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr4)
    } else if (num_model == 154) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+epoch*sin(16*pi/t1*epoch)+epoch*cos(16*pi/t1*epoch), tr4)
    } else if (num_model == 155) {
        lmX <- lm(aux ~ epoch+epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+epoch*sin(16*pi/t1*epoch)+epoch*cos(16*pi/t1*epoch)+epoch*x_sim+epoch*y_sim+epoch*z_sim+epoch*Vx_sim+epoch*Vy_sim+epoch*Vz_sim, tr4)
    } else if (num_model == 156) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+sin(12*pi/t1*epoch)+cos(12*pi/t1*epoch)+sin(14*pi/t1*epoch)+cos(14*pi/t1*epoch)+sin(16*pi/t1*epoch)+cos(16*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr4)
    } else if (num_model == 157) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+sin(12*pi/t1*epoch)+cos(12*pi/t1*epoch)+sin(14*pi/t1*epoch)+cos(14*pi/t1*epoch)+sin(16*pi/t1*epoch)+cos(16*pi/t1*epoch), tr4)
    }
  
  #9 armónios
      else if (num_model == 158) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+epoch*sin(16*pi/t1*epoch)+epoch*cos(16*pi/t1*epoch)+epoch*sin(18*pi/t1*epoch)+epoch*cos(18*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr4)
    } else if (num_model == 159) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+epoch*sin(16*pi/t1*epoch)+epoch*cos(16*pi/t1*epoch)+epoch*sin(18*pi/t1*epoch)+epoch*cos(18*pi/t1*epoch), tr4)
    } else if (num_model == 160) {
        lmX <- lm(aux ~ epoch+epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+epoch*sin(16*pi/t1*epoch)+epoch*cos(16*pi/t1*epoch)+epoch*sin(18*pi/t1*epoch)+epoch*cos(18*pi/t1*epoch)+epoch*x_sim+epoch*y_sim+epoch*z_sim+epoch*Vx_sim+epoch*Vy_sim+epoch*Vz_sim, tr4)
    } else if (num_model == 161) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+sin(12*pi/t1*epoch)+cos(12*pi/t1*epoch)+sin(14*pi/t1*epoch)+cos(14*pi/t1*epoch)+sin(16*pi/t1*epoch)+cos(16*pi/t1*epoch)+sin(18*pi/t1*epoch)+cos(18*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr4)
    } else if (num_model == 162) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+sin(12*pi/t1*epoch)+cos(12*pi/t1*epoch)+sin(14*pi/t1*epoch)+cos(14*pi/t1*epoch)+sin(16*pi/t1*epoch)+cos(16*pi/t1*epoch)+sin(18*pi/t1*epoch)+cos(18*pi/t1*epoch), tr4)
    }
  
  #10 armónicos
      else if (num_model == 163) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+epoch*sin(16*pi/t1*epoch)+epoch*cos(16*pi/t1*epoch)+epoch*sin(18*pi/t1*epoch)+epoch*cos(18*pi/t1*epoch)+epoch*sin(20*pi/t1*epoch)+epoch*cos(20*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr4)
    } else if (num_model == 164) {
        lmX <- lm(aux ~ epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+epoch*sin(4*pi/t1*epoch)+epoch*cos(4*pi/t1*epoch)+epoch*sin(6*pi/t1*epoch)+epoch*cos(6*pi/t1*epoch)+epoch*sin(8*pi/t1*epoch)+epoch*cos(8*pi/t1*epoch)+epoch*sin(10*pi/t1*epoch)+epoch*cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+epoch*sin(16*pi/t1*epoch)+epoch*cos(16*pi/t1*epoch)+epoch*sin(18*pi/t1*epoch)+epoch*cos(18*pi/t1*epoch)+epoch*sin(20*pi/t1*epoch)+epoch*cos(20*pi/t1*epoch), tr4)
    } else if (num_model == 165) {
        lmX <- lm(aux ~ epoch+epoch*sin(2*pi/t1*epoch)+epoch*cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+epoch*sin(12*pi/t1*epoch)+epoch*cos(12*pi/t1*epoch)+epoch*sin(14*pi/t1*epoch)+epoch*cos(14*pi/t1*epoch)+epoch*sin(16*pi/t1*epoch)+epoch*cos(16*pi/t1*epoch)+epoch*sin(18*pi/t1*epoch)+epoch*cos(18*pi/t1*epoch)+epoch*sin(20*pi/t1*epoch)+epoch*cos(20*pi/t1*epoch)+epoch*x_sim+epoch*y_sim+epoch*z_sim+epoch*Vx_sim+epoch*Vy_sim+epoch*Vz_sim, tr4)
    } else if (num_model == 166) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+sin(12*pi/t1*epoch)+cos(12*pi/t1*epoch)+sin(14*pi/t1*epoch)+cos(14*pi/t1*epoch)+sin(16*pi/t1*epoch)+cos(16*pi/t1*epoch)+sin(18*pi/t1*epoch)+cos(18*pi/t1*epoch)+sin(20*pi/t1*epoch)+cos(20*pi/t1*epoch)+x_sim+y_sim+z_sim+Vx_sim+Vy_sim+Vz_sim, tr4)
    } else if (num_model == 167) {
        lmX <- lm(aux ~ epoch+sin(2*pi/t1*epoch)+cos(2*pi/t1*epoch)+sin(4*pi/t1*epoch)+cos(4*pi/t1*epoch)+sin(6*pi/t1*epoch)+cos(6*pi/t1*epoch)+sin(8*pi/t1*epoch)+cos(8*pi/t1*epoch)+sin(10*pi/t1*epoch)+cos(10*pi/t1*epoch)+sin(12*pi/t1*epoch)+cos(12*pi/t1*epoch)+sin(14*pi/t1*epoch)+cos(14*pi/t1*epoch)+sin(16*pi/t1*epoch)+cos(16*pi/t1*epoch)+sin(18*pi/t1*epoch)+cos(18*pi/t1*epoch)+sin(20*pi/t1*epoch)+cos(20*pi/t1*epoch), tr4)
    }
  
  if (num_model < 168){ #Modelo predicho = simulado
    if (!pred) score(predict(lmX, val), unlist(val[,coord+3]))
    else predict(lmX, tst)
  }
  else {
    if (!pred) score(unlist(val[,coord+9]), unlist(val[,coord+3]))
    else unlist(tst[,coord+3])
  }
}
```



Get best model for each satelite
```{r}
for (i in 0:599) {
  print(i)
  mods <- data.frame(sat_id=i,x=0,y=0,z=0,Vx=0,Vy=0,Vz=0)
  scores <- data.frame(sat_id=i,x=0,y=0,z=0,Vx=0,Vy=0,Vz=0)
  for (coo in 1:6) {
    best <- 0
    mx <- 0
    for (mod in  c(48:167)) {
      sc <- model(i, coo, mod)
      if (sc > mx) {
        mx <- sc
        best <- mod
      }
    }
    mods[,coo+1] <- best
    scores[,coo+1] <- mx
  }
  if (i == 0) {
    ans <- mods
    ans2 <- scores
  } else {
    ans <- rbind(ans, mods)
    ans2 <- rbind(ans2, scores)
  }
}

write_csv(ans, "models.csv", quote=F)
write_csv(ans2, "scores.csv", quote=F)
```



Read best models
```{r}
ans <- read_csv("models.csv")
```



Predictions
```{r}
for (i in unique(test$sat_id)) {
  print(i)
  pred <- filter(test, sat_id==i)
  for (coor in 1:6) {
    pred[,coor+3] <- model(i, coor, ans[i+1, coor+1], T)
  }
  
  if (i == unique(test$sat_id)[1]) sol <- data.frame(id=pred$id, x=unlist(pred[,1+3]), y=unlist(pred[,2+3]), z=unlist(pred[,3+3]), Vx=unlist(pred[,4+3]), Vy=unlist(pred[,5+3]), Vz=unlist(pred[,6+3]))
  else sol <- rbind(sol, data.frame(id=pred$id, x=unlist(pred[,1+3]), y=unlist(pred[,2+3]), z=unlist(pred[,3+3]), Vx=unlist(pred[,4+3]), Vy=unlist(pred[,5+3]), Vz=unlist(pred[,6+3])))
}
```


Write submission file
```{r}
write_csv(sol, "Submission.csv", quote=F)
```


